\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{setspace}

\pagestyle{fancy}

\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\begin{document}

\centering\textbf{\Large AUSTIN ROVGE}

\centering\href{mailto:austinrovge@gmail.com}{austinrovge@gmail.com} • (262) 313-8015

\centering\href{https://github.com/austinrovge}{github.com/austinrovge} • \href{https://ajr.dev/about}{ajr.dev/about} • \href{https://linkedin.com/in/austinrovge}{linkedin.com/in/austinrovge}

\section{SKILLS}
\begin{itemize}
   \setlength\itemsep{-0.25em}
   \item{
     Languages: Bash, C, C\#, CSS, HTML, Java, MySQL, Node, Python, React, Redux, Ruby, TypeScript
   }
   \item{
     Tools \& Practices: AWS, Docker, DynamoDB, Elasticsearch, Git, GitLab CI, Jira, NPM, Scrum, Terraform
   }
\end{itemize}

\section{EXPERIENCE}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  Software Engineer & June 2021 – Present\\
  Software Engineer Intern & June 2019 – June 2021\\
  Direct Supply & Milwaukee, WI\\
\end{tabular*}
\begin{itemize}
   \setlength\itemsep{-0.25em}
   \item{
     Worked with the Supply Chain team to determine requirements and metric thresholds for displaying data to
the service providers based on their performance for previously completed work items.
   }
   \item{
Utilized AWS Elasticsearch to improve filtering for assets by properties and to quickly return large lists of
matching data to the primary asset web service, lowering asset search response times for the end user.
   }
      \item{
Assisted in translating UI mockups created by the development, sourcing, and UX teams to their final frontend versions using randomly generated placeholder data.
   }
\end{itemize}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  Software Engineer Intern & September 2018 – May 2019\\
  Wickidcool Software & Milwaukee, WI\\
\end{tabular*}
\begin{itemize}
   \setlength\itemsep{-0.25em}
   \item{
Remotely collaborated with other developers using Git to minimize merge conflicts and implement features
simultaneously, improving productivity and reduced development timeline.
   }
   \item{
Collaborated in development for the front-end using ReactJS and Redux to handle data received from the
Node.js back-end of the application, populating it with data from other event services.
   }
      \item{
Created and altered database tables to store data for events obtained from various other event management
site APIs, allowing for the publishing of an event to multiple services instantly.
   }
\end{itemize}

\section{EDUCATION}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  Milwaukee School of Engineering & Graduated May 2021\\
  B.S. Software Engineering & Milwaukee, WI\\
  Minor in User Experience & GPA: 3.5 / Major GPA: 3.7
\end{tabular*}

\section{PROJECTS}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  Fluoroscopy Simulator – Medical College of Wisconsin & September 2019 – May 2020
\end{tabular*}
\begin{itemize}
   \setlength\itemsep{-0.25em}
   \item{
Created UI mockups detailing the user workflow and consulted with UX professors and application users to
iterate on the design prior to starting development work on the application.
   }
   \item{
Architected the full-stack web application solution based on requirement gathering sessions with the product
owner and other stakeholders, improving on the original POC developed prior to our team’s involvement.
   }
      \item{
Researched image analysis techniques using OpenCV, documenting the process in Jupyter notebooks.
Viable options were produced to calculate the distance between two points in 3D space and returning the
image to the client as a static image.
   }
\end{itemize}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  At The Control – FIRST Robotics Streaming Site & September 2015 – August 2017
\end{tabular*}
\begin{itemize}
   \setlength\itemsep{-0.25em}
   \item{
Created and altered database tables to store data obtained from the FRC Events API to minimize the update
requests made and allow users to see real-time event updates for live matches.
   }
   \item{
Trained new members to have basic web client-server understanding, allowing them to independently
contribute to the project with newly gained skills and comprehension.
   }
      \item{
 Designed a new application architecture with industry mentors to improve performance and maintainability.
   }
\end{itemize}
\end{document}
